Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)

### 2022-09-24 paper.tex
Updated Experiments
Improved experiment description.

            The goal of the first experiment was to confirm that this paper’s
            proposed strategy obtained improved results over our basic
            technique, which created a new population with a random generation
            of a new set of candidate solutions. We chose Ackley as the first
            Classic Benchmark Function for Optimization to test our algorithm
            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
            Box and Whisker chart, and we summarized the results in
            Table~\ref{tab.fun_ackley5} and Table~\ref{tab.fun_ackley10} (for
            five and ten dimensions, respectively).

@@

            As our second experiment to further validate and prove our
            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_bohachevsky5} and
            Table~\ref{tab.fun_bohachevsky10} (for five and ten dimensions,
            respectively). Due to the observation and analysis of these
            results, we identify our proposed strategy obtained solutions in
            the same order as the traditional Xover Mutation, in a
            significantly reduced number of evaluations.

@@

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_griewank5} and
            Table~\ref{tab.fun_griewank10} (for five and ten dimensions,
            respectively). With this analysis, we confirmed our strategy
            continued to obtain solutions in the same order as expected, in a
            reduced number of evaluations, in less time.

@@

            This experiment's goal was to follow and study the behavior of our
            proposed strategy, to repeat the results in the same order as
            expected, in a reduced number of both time and evaluations. We
            selected Rastrigin Classic Benchmark Function for Optimization for
            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Table~\ref{tab.fun_rastrigin5} and
            Table~\ref{tab.fun_rastrigin10} (for five and ten dimensions,
            respectively).

@@

            For our fifth experiment we chose the Sphere Classic Benchmark
            Function for Optimization. Even though the sphere function is
            considered one of the simplest to solve, the same behavior was
            consistent for the algorithm, where it showed a reduced number of
            evaluations and execution time. We can confirm this affirmation
            with the results shown in this experiment.
            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
            Whisker chart, where we summarized the results in
            Table~\ref{tab.fun_sphere5} and Table~\ref{tab.fun_sphere10} (for
            five and ten dimensions, respectively).

@@

            AQUI.

>>>>

            The goal of the first experiment was to confirm that this paper’s
            proposed strategy obtained improved results over our basic
            technique, which created a new population with a random generation
            of a new set of candidate solutions. We chose Ackley as the first
            Classic Benchmark Function for Optimization to test our algorithm
            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
            Box and Whisker chart, and we summarized the results in
            Tables~\ref{tab.fun_ackley5} and~\ref{tab.fun_ackley10} (for five 
            and ten dimensions, respectively).

@@

            As our second experiment to further validate and prove our
            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_bohachevsky5} and~\ref{tab.fun_bohachevsky10} 
            (for five and ten dimensions, respectively). Due to the observation 
            and analysis of these results, we identify our proposed strategy 
            obtained solutions in the same order as the traditional Xover Mutation, 
            in a significantly reduced number of evaluations.

@@

            The third experiment objective was to confirm Animal Life Cycle
            Algorithm continued finding solutions in a reduced number of
            evaluations. For this test, we selected the Griewank Benchmark
            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
            (for five and ten dimensions, respectively). With this analysis, 
            we confirmed our strategy continued to obtain solutions in the same 
            order as expected, in a reduced number of evaluations, in less time.

@@

            This experiment's goal was to follow and study the behavior of our
            proposed strategy, to repeat the results in the same order as
            expected, in a reduced number of both time and evaluations. We
            selected Rastrigin Classic Benchmark Function for Optimization for
            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
            corresponding Box and Whisker chart, where we summarized the
            results in Tables~\ref{tab.fun_rastrigin5} and~\ref{tab.fun_rastrigin10} 
            (for five and ten dimensions, respectively).

@@

            For our fifth experiment we chose the Sphere Classic Benchmark
            Function for Optimization. Even though the sphere function is
            considered one of the simplest to solve, the same behavior was
            consistent for the algorithm, where it showed a reduced number of
            evaluations and execution time. We can confirm this affirmation
            with the results shown in this experiment.
            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
            Whisker chart, where we summarized the results in
            Tables~\ref{tab.fun_sphere5} and~\ref{tab.fun_sphere10} (for
            five and ten dimensions, respectively).

@@

            The goal of our sixth and last experiment was to study the behavior
            of the Animal Life-Cycle Algorithm when tested with the Rosenbrock
            Benchmark Function for Optimization. From all of our previous
            evaluation functions, Rosenbrock presented the most difficult
            challenge for our algorithm. This test facilitated the
            differentiation between the three compared strategies because the
            solutions found were in different numeric order. After all tests,
            the Elite Projection proved to be the best alternative. We can
            corroborate this by analyzing Figures~\ref{fig.fun_rosenbrock_5d}
            and~\ref{fig.fun_rosenbrock_10d}, which shows its corresponding Box
            and Whisker chart. We present the summarized results in
            Tables~\ref{tab.fun_rosenbrock5} and~\ref{tab.fun_rosenbrock10}
            (for five and ten dimensions, respectively).
